\documentclass[]{deedy-resume-openfont}
\begin{document}
\lastupdated

\namesection{Thomas}{Klinger}{ \urlstyle{same}\url{http://github.com/teekaay} \\
\href{mailto:2klinger@informatik.uni-hamburg.de}{2klinger@informatik.uni-hamburg.de} | 040-87605114
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{University of Hamburg}
\descript{MSc in Computer Science}
\location{Expected Dec 2018}
\sectionsep

\descript{BSc in Computer Science}
\location{Expected June 2016}
% Courses
\location{Grade: 2.7}
\sectionsep

\subsection{Vincent-Lübeck-Gymnasium Stade}
\location{Grad. June 2011|  Stade, GER}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Github:// \href{https://github.com/teekaay}
{\custombold{teekaay}} \\
Twitter://  \href{https://twitter.com/tee_okay}{\custombold{@tee\_okay}} \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\subsection{Graduate}
Neural Networks \\
Requirements Engineering \\
\sectionsep

\subsection{Undergraduate}
Data Mining \\
Machine Learning (graduate course) \\
Probability Theory I \& II \\ 
Brain Modelling

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
Bash \textbullet{} Python (NumPy, scikit-learn) \textbullet{} JavaScript (Angular, React, ES6) \textbullet{} TypeScript \textbullet{} SASS \& CSS \textbullet{} \LaTeX \textbullet{}
\sectionsep

\subsection{Software}
OSX \textbullet{} Linux \textbullet{} Matlab \textbullet{}
Vim

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{Informatics Library}
\descript{| Working student }
\location{April 2013 – February 2016 | Hamburg, GER}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Provided help in literature research to students and researchers.
\item Gathered in-depth knowledge of the scientific publishing business 
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Research}
\runsubsection{Bachelor Thesis}
\descript{}
\location{Winter Term 2015/2016 - current | Hamburg, GER}
Title: \textsc{Analyzing Spectral Data using Similarity Search} \\
Applying machine learning algorithms to chemical data sets, especially
chromatographic data.  
\sectionsep

\runsubsection{Practical Course Implementing a Microcontroller}
\descript{| Compiler Designer}
\location{Winter Term 2015/2016 - current | Hamburg, GER}
Part of a group that implemented a Lisp machine in VHDL. Worked
on a native compiler for the machine in TypeScript. Code available 
in GitHub repository. 

\runsubsection{Seminar Brain Modeling}
\descript{}
\location{Summer Term 2015 | Hamburg, GER}
Worked on applying game theoretical concepts to reinforcement learning in uncertain environments. \\
Publication title: \textsc{Reward-based learning in cooperative games}. Paper submitted to ResearchGate. 
\sectionsep


\end{minipage} 
\end{document}  \documentclass[]{article}